### 2019-11-20 ch2_dyngen/content.tex
update

A cell consists of a set of molecules, the abundance of which are affected by a set of reactions: transcription, splicing, translation, and degradation (Figure \ref{fig:simplecyclic}A). 
A gene regulatory network (GRN) define the reactions that are allowed to occur (Figure \ref{fig:simplecyclic}B), and is constructed such that a cell will develop over time (Figure \ref{fig:simplecyclic}C--D).
The likelihood of a reaction occurring is a function of the abundance of key molecules involved in each reaction (Figure \ref{fig:simplecyclic}E).

@@

\paragraph{Step 1, sampling the transcription factors (TF).} The TFs are the main drivers of the molecular changes in the simulation. The user provides a backbone and the number of TFs to generate. Each TF is assigned to a module such that each module has at least $x$ parameters (default $x=1$). A TF inherits the 'burn' and 'basal expression' from the module in belongs to.

@@

\paragraph{Step 3, sampling the target subnetwork.} 
A user-defined number of target genes are added to the GRN. Target genes regulated by a TF or another target gene, but is always downstream of at least one TF. To sample the interactions between target genes, one of the many FANTOM5 \cite{lizio_gatewaysfantom5promoter_2015} GRNs is sampled. The currently existing TFs are mapped to regulators in the FANTOM5 GRN. The targets are drawn from the FANTOM5 GRN, weighted by their page rank value. For each target, at most $x$ regulators are sampled from the induced FANTOM5 GRN (default $x=5$). The interactions connecting a target gene and its regulators are added the GRN.

>>>>

A cell consists of a set of molecules, the abundance of which are affected by a set of reactions: transcription, splicing, translation, and degradation (Figure \ref{fig:simplecyclic}A). 
A gene regulatory network (GRN) defines the reactions that are allowed to occur (Figure \ref{fig:simplecyclic}B), and is constructed such that a cell will develop over time (Figure \ref{fig:simplecyclic}C--D).
The likelihood of a reaction occurring is a function of the abundance of key molecules involved in each reaction (Figure \ref{fig:simplecyclic}E).

@@

\paragraph{Step 1, sampling the transcription factors (TF).} The TFs are the main drivers of the molecular changes in the simulation. The user provides a backbone and the number of TFs to generate. Each TF is assigned to a module such that each module has at least $x$ parameters (default $x=1$). A TF inherits the 'burn' and 'basal expression' from the module it belongs to.

@@

\paragraph{Step 3, sampling the target subnetwork.} 
A user-defined number of target genes are added to the GRN. Target genes are regulated by a TF or another target gene, but is always downstream of at least one TF. To sample the interactions between target genes, one of the many FANTOM5 \cite{lizio_gatewaysfantom5promoter_2015} GRNs is sampled. The currently existing TFs are mapped to regulators in the FANTOM5 GRN. The targets are drawn from the FANTOM5 GRN, weighted by their page rank value. For each target, at most $x$ regulators are sampled from the induced FANTOM5 GRN (default $x=5$). The interactions connecting a target gene and its regulators are added the GRN.

### 2019-11-20 ch6_bred/content.tex
update

Computing the case-wise feature importances of a tree consists of the following 8 steps (Figure~\ref{fig:fimp}).
The 'randomness' of a Random Forest is due to only using a subset of the samples in the dataset in order to build a single decision tree. The samples are split into two groups, the 'in-bag' data and the 'out-of-bag' data (Figure~\ref{fig:fimp}A). A decision tree \cite{breiman_classificationregressiontrees_1984} is trained on the in-bag expression of the potential regulators in trying to predict the in-bag target gene expression (Figure~\ref{fig:fimp}B). The target expression of the out-of-bag samples is predicted using the decision tree (Figure~\ref{fig:fimp}C), and the squared error between the real and target expression is computed (Figure~\ref{fig:fimp}D). For each sample in the out-of-bag set, this vector represents how well the decision tree was able to predict the expression of the target gene.

@@

A moderately-sized dataset could contain $M=10'000$ samples, $N=2'000$ regulators, and $P=10'000$ target genes. Due to memory constrains, only interactions with an average importance value (across all samples) higher than a minimum threshold are retained.

@@

Next, KD-trees are used to calculate the $k$NN graph efficiently. The cases in the dataset are visualised and clusted using the Fruchterman-Reingold \cite{fruchterman_graphdrawingforcedirected_1991} and Louvain clustering \cite{blondel_fastunfoldingcommunities_2008}, respectively.

>>>>

Computing the case-wise feature importances of a tree consists of the following 8 steps (Figure~\ref{fig:fimp}).
The 'randomness' of a Random Forest is in part due to using a subset of the samples in the dataset in order to build a single decision tree. The samples are split into two groups, the 'in-bag' data and the 'out-of-bag' data (Figure~\ref{fig:fimp}A). A decision tree \cite{breiman_classificationregressiontrees_1984} is trained on the in-bag expression of the potential regulators in trying to predict the in-bag target gene expression (Figure~\ref{fig:fimp}B). The target expression of the out-of-bag samples is predicted using the decision tree (Figure~\ref{fig:fimp}C), and the squared error between the real and target expression is computed (Figure~\ref{fig:fimp}D). For each sample in the out-of-bag set, this vector represents how well the decision tree was able to predict the expression of the target gene.

@@

A moderately-sized dataset could contain $M=10'000$ samples, $N=2'000$ regulators, and $P=10'000$ target genes. Due to memory constraints, only interactions with an average importance value (across all samples) higher than a minimum threshold are retained.

@@

Next, KD-trees are used to calculate the $k$NN graph efficiently. The cases in the dataset are visualised and clustered using the Fruchterman-Reingold \cite{fruchterman_graphdrawingforcedirected_1991} and Louvain clustering \cite{blondel_fastunfoldingcommunities_2008}, respectively.
